RDF Constraint Types to Ensure High Data Quality

### 2015-04-29 paper/paper7/paper7.tex
section 4

According to the complexity of constraint types, the complete set of \emph{constraint types} ($\mathcal{CT}$) encompasses three disjoint \emph{sets of constraint types}:
\begin{enumerate}
	\item $\mathcal{CT}_{B}$: \textbf{\emph{Basic Constraint Types}}
	\item $\mathcal{CT}_{S}$: \textbf{\emph{Simple Constraint Types}}
	\item $\mathcal{CT}_{C}$: \textbf{\emph{Complex Constraint Types}}
\end{enumerate}

The modeling languages \emph{RDF}, \emph{RDFS}, and \emph{OWL} are typically used to define vocabularies.
\emph{Basic constraint types} ($\mathcal{CT}_{B}$) 
denotes the set of constraint types whose constraints 
can be extracted completely automatically out of vocabularies.
As vocabularies have been specified using \emph{RDF}, \emph{RDFS}, and \emph{OWL},
\emph{basic constraints} ensure that the data is consistent with the intended syntaxes, semantics, and integrity of vocabularies' data models.
%The {\em existential quantification} (\emph{R-86}) 
%\ms{Study $\equiv$ $\exists$ product.LogicalDataSet} (\emph{DL}), e.g., restricts studies to contain at least one data set which is expressible in OWL 2:
\emph{Minimum qualified cardinality restrictions} (\emph{R-74}), e.g., guarantee that individuals of given classes are connected by particular properties to at least n different individuals/literals of certain classes or data ranges.
This way, it is expressible in \emph{OWL 2} that a \emph{phdd:TableStructure} has (\emph{phdd:column}) at least one \emph{phdd:Column}:
\begin{ex}
[   a owl:Restriction ; rdfs:subClassOf TableStructure ;
    owl:minQualifiedCardinality 1 ;
    owl:onProperty column ;
    owl:onClass Column ] .
\end{ex}

\emph{Simple constraint types} ($\mathcal{CT}_{S}$) is the set of constraint types whose constraints can be easily defined without much effort in addition to $\mathcal{CT}_{B}$ constraints.
{\emph{Data property facets} (\emph{R-46}) is an example of an $\mathcal{CT}_{S}$ constraint type which enables to declare frequently needed facets for data properties in order to validate input against simple conditions including min/max values, regular expressions, and string length.
The abstract of series/studies, e.g., should have a minimum length.

\emph{Complex constraint types} ($\mathcal{CT}_{C}$) encompass constraint types for which the definition of constraints is rather complex and cannot be derived from vocabulary definitions.
Complex constraints show the importance of constraint languages enabling to describe more complex constraints.
For assessing the quality of thesauri, e.g., we concentrate on the graph-based structure and apply graph- and network-analysis techniques.
An example of such constraints of the constraint type \emph{structure} is that 
a thesaurus should not contain many orphan concepts, i.e., concepts without any associative or hierarchical relations, lacking context information valuable for search.

@@

\emph{SBE} experts determined the default \textbf{\emph{severity level}} (\emph{R-158}) for each constraint to indicate how serious the violation of the constraint is.\tb{of the 213 constraints}
We propose an extensible metric to measure the continuum of severity levels ranging from $\mathcal{SL}_{0}$ to $\mathcal{SL}_{2}$.
According to the constraints' default severity level the complete set of constraints ($\mathcal{C}$) encompasses three disjoint \emph{sets of constraints}:
\begin{itemize}
	\item $\mathcal{SL}_{0}$: set of constraints with \textbf{severity level \emph{informational}}
	\item $\mathcal{SL}_{1}$: set of constraints with \textbf{severity level \emph{warning}}
	\item $\mathcal{SL}_{2}$: set of constraints with \textbf{severity level \emph{error}}
\end{itemize}
Violations of $\mathcal{SL}_{0}$ constraints point to desirable data improvements to achieve RDF representations which are ideal in terms of syntax and semantics of used vocabularies. 
Data not conforming to $\mathcal{SL}_{1}$ and $\mathcal{SL}_{2}$ constraints is syntactically and/or semantically not correctly represented.
The difference between $\mathcal{SL}_{1}$ and $\mathcal{SL}_{2}$ constraints is that data, not conforming to $\mathcal{SL}_{1}$ but conforming to $\mathcal{SL}_{2}$ constraints, could be processed further,
whereas data, not corresponding to $\mathcal{SL}_{2}$ constraints, cannot be processed further after validation. 
As constraints of $\mathcal{CT}_{B}$ constraint types are derived from explicitly stated semantics of vocabularies, 
their default severity levels are in most cases very strong ($\mathcal{SL}_{2}$) and 
in average stronger than the severity levels of constraints assigned to $\mathcal{CT}_{S}$ and $\mathcal{CT}_{C}$ constraint types.
As a consequence, violating many constraints of $\mathcal{CT}_{B}$ constraint types is an indicator for bad (meta)data quality\footnote{For simplicity reasons, we only assign severity levels to $\mathcal{CT}_{B}$ constraints in this paper in case they differ from $\mathcal{SL}_{2}$.}.

>>>>

According to the complexity of constraint types, the complete set of \emph{constraint types} encompasses three disjoint \emph{sets of constraint types}:
\begin{enumerate}
	\item \textbf{\emph{Vocabulary Constraint Types}}
	\item \textbf{\emph{Simple Constraint Types}}
	\item \textbf{\emph{Complex Constraint Types}}
\end{enumerate}

The modeling languages \emph{RDF}, \emph{RDFS}, and \emph{OWL} are typically used to define vocabularies.
\emph{Vocabulary constraint types}
denotes the set of constraint types whose constraints 
can be extracted completely automatically out of the formal specifications of vocabularies.
As vocabularies have been specified using \emph{RDF}, \emph{RDFS}, and \emph{OWL},
\emph{vocabulary constraints} ensure that the data is consistent with the intended syntaxes, semantics, and integrity of vocabularies' data models.
%The {\em existential quantification} (\emph{R-86}) 
%\ms{Study $\equiv$ $\exists$ product.LogicalDataSet} (\emph{DL}), e.g., restricts studies to contain at least one data set which is expressible in OWL 2:
\emph{Minimum qualified cardinality restrictions} (\emph{R-74}), e.g., guarantee that individuals of given classes are connected by particular properties to at least n different individuals/literals of certain classes or data ranges.
This way, it is expressible in \emph{OWL 2} that a \emph{phdd:TableStructure} has (\emph{phdd:column}) at least one \emph{phdd:Column}:
\begin{ex}
[   a owl:Restriction ; rdfs:subClassOf TableStructure ;
    owl:minQualifiedCardinality 1 ;
    owl:onProperty column ;
    owl:onClass Column ] .
\end{ex}

\emph{Simple} and \emph{complex constraints} are in contrast to \emph{vocabulary constraints} not explicitly defined within formal specifications of vocabularies.
\emph{Simple} and \emph{complex constraints} are defined according to textual descriptions of the intended semantics of vocabularies.  
\emph{Simple constraint types} is the set of constraint types whose constraints can be easily defined without much effort in addition to \emph{vocabulary constraints}.
{\emph{Data property facets} (\emph{R-46}) is an example of a \emph{simple constraint type} which enables to declare frequently needed facets for data properties in order to validate input against simple conditions including min/max values, regular expressions, and string length.
The abstract of series/studies, e.g., should have a minimum length.

\emph{Complex constraint types} encompass constraint types for which the definition of constraints is rather complex and cannot be derived from vocabulary definitions.
For assessing the quality of thesauri, e.g., we concentrate on the graph-based structure and apply graph- and network-analysis techniques.
An example of such constraints of the constraint type \emph{structure} is that 
a thesaurus should not contain many orphan concepts, i.e., concepts without any associative or hierarchical relations, lacking context information valuable for search. 
\emph{Complex constraints} show the importance to develop constraint languages enabling to describe more complex constraints.

@@

\emph{SBE} experts determined the default \textbf{\emph{severity level}} (\emph{R-158}) for each of the 246 constraints to indicate how serious the violation of the constraint is.
We propose an extensible metric to measure the continuum of severity levels ranging from \emph{informational} to \emph{error}.
According to the constraints' default severity level, the complete set of constraints encompasses three disjoint \emph{sets of constraints}:
\begin{itemize}
	\item \textbf{\emph{informational constraints}}: constraints with severity level {\emph{informational}
	\item \textbf{\emph{warning constraints}}: constraints with severity level \emph{warning}
	\item \textbf{\emph{error constraints}}: constraints with severity level \emph{error}
\end{itemize}
Violations of \emph{informational constraints} point to desirable but not necessary data improvements to achieve RDF representations which are ideal in terms of syntax and semantics of used vocabularies. 
Data not conforming to \emph{warning} and \emph{error constraints} is syntactically and/or semantically not correctly represented.
The difference between \emph{warning} and \emph{error constraints} constraints is that data, not conforming to \emph{warning constraints} but conforming to \emph{error constraints}, could be processed further,
whereas data, not corresponding to \emph{error constraints}, cannot be processed further after validation. 
As constraints of \emph{vocabulary constraint types} are derived from explicitly stated semantics of vocabularies, 
their default severity levels are in most cases very strong (\emph{error}) and 
in average stronger than the severity levels of constraints assigned to \emph{simple and complex constraint types}.
As a consequence, violating many constraints of \emph{vocabulary constraint types} is an indicator for bad (meta)data quality\footnote{For simplicity reasons, we only assign severity levels to \emph{vocabulary constraints} in this paper in case they differ from \emph{error constraints}.}.
